biological data preperation

### 2018-09-19 src/biological_data_prep.Rmd
amo_sample added

to test this just subset some of your species data...
```{r}
test <- data_aea <- data_aea[data_aea$year < 2000,  ]
```

ok now do something...

subset cols 1:13
```{r}
testamo <- amo <- amo[ ,1:13]
testamo
```

```{r}
testamo <- reshape(testamo, 
  varying = c("1", "2","3", "4", "5", "6", "7", "8", "9", "10", "11", "12"),
  v.names = "value",
  direction = "long")

testamo.sort <- testamo[order(testamo$year),]
testamo
```

ok... soo now something like
where test$year = testamo$year AND test$month = testamo$time
  extract value
    add to new test$amo_sample

>>>>

Start with the month data first...subset cols 1:13 (where the year and month data are held)
```{r}
amo_yrmt <- amo[ ,1:13]
amo_yrmt
```

```{r}
amo_yrmt <- reshape(amo_yrmt, 
  varying = c("1", "2","3", "4", "5", "6", "7", "8", "9", "10", "11", "12"),
  v.names = "value",
  direction = "long")

amo_yrmt.sort <- amo_yrmt[order(amo_yrmt$year),]
amo_yrmt
```
rename time to month.. and value to amo_sample
```{r}
colnames(amo_yrmt)[2] <- "month"
colnames(amo_yrmt)[3] <- "amo_sample"
amo_yrmt
```

now match the year and the month in the two dataframes, and populate the species dataset (data_aea) with amo_sample
```{r}
data_aea <- merge(x = data_aea, y = amo_yrmt[ , c("year", "month", "amo_sample")], by = c("year", "month"), all.x = TRUE)
data_aea
```

ok
